Fail Faster

### 2025-03-24 paper/paper.tex
fix figs
wibbling

\newif\ifdraft\drafttrue{}
\newif\iflater\latertrue{}
\newif\ifaftersubmission\aftersubmissionfalse{}
\newif\ifsilly\sillyfalse{}

@@

With a sense of two main inefficiences in generator libraries, we set out in this section to investigate solutions.
We begin with a quick tour through multi-stage programming (\ref{xx}),
then incrementally build \camlname, layering on features and
functionality  (\ref{xx}).
Last, we present a controlled experiment demonstrating how a
faster \rand{} leads to failing faster  (\ref{xx}).

@@

\subsection{Design of a Staged Generator DSL}
\label{subsection:basic-design}
To build a staged version of a generator DSL, we want to rewrite the the generator
combinators to do as much as possible at compile time.
The compile-time stage will then produce simplified code, free of any DSL abstraction, that can be compiled and run
with different sizes and seeds.
Our job is thus to carefully bisect the DSL, determining which inputs to generator
combinators are known statically (and can be part of the compile time stage) and
which parts are only known at run time (and must be treated as \texttt{code}).
In the staging literature, this task is known as ``binding-time
analysis,'' \cite{jones1993partial}, and it is more art than
science.\bcp{Why do we need to say that last part?}

>>>>

\newif\ifdraft\drafttrue{}
\newif\iflater\latertrue{}
\newif\ifaftersubmission\aftersubmissionfalse{}
\newif\ifsilly\sillytrue{}

@@

With a sense of two main inefficiences in generator libraries, we set out in this section to investigate solutions.
We begin with a quick tour through multi-stage programming (Section~\ref{subsection:msp}),
then incrementally build \camlname, layering on features and
functionality  (Sections~\ref{subsection:basic-design} through \ref{subsection:type-derived}).
Last, we present a controlled experiment demonstrating how a
faster \rand{} leads to failing faster  (\ref{subsection:faster-rng}).

@@

\subsection{Design of a Staged Generator DSL}
\label{subsection:basic-design}
To build a staged version of a generator DSL, we want to rewrite the the generator
combinators to do as much as possible at compile time.
The compile-time stage will then produce simplified code, free of any DSL abstraction, that can be compiled and run
with different sizes and seeds.
Our job is thus to carefully bisect the DSL, determining which inputs to generator
combinators are known statically (and can be part of the compile time stage) and
which parts are only known at run time (and must be treated as \texttt{code}).
In the staging literature, this task is known as ``binding-time
analysis,'' \cite{jones1993partial}.
